Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-20 Response to reviewers.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment: Response to Reviewers\' comments}

\noindent
Dear Sirs,\\

First, we would like to express our gratitude to the Editor in Chief,
the editorial team and the reviewers whose valuable comments on this
paper have significantly improved its quality. All suggestions are
highly appreciated and we have added a line in the acknowledgements
section thanking the reviewers. \\

In this new revision, we have carefully addressed all the comments in
the new version of the paper. We will enumerate below these comments
(in italics) and our corresponding response. \\

We look forward to hearing from you about the final decision on our paper. \\

@@

Our main contribution is, thus, to develop a methodology to 
process book sales data in order to first find out relevant 
variables and then use these variables to process data so that 
the publisher, using them, can estimate sales and from them order 
a specific print run, instead of standard ones, which are around 
300 copies for standard books and around 5000 for those that are 
considered, in advance, best sellers.

Also, in the next-to-last paragraph, we have laid out our 
methodology and the main contributions of this paper.
\end{verbatim}

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommend systems
have been added to the future works, at the end of Section 7 
(see page 19).
\end{verbatim}

### 2016-08-20 Response to reviewers.tex

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
THIS HAS TO BE DONE.
\end{verbatim}

~\\
\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ? For RF, how many trees are set? }

\begin{verbatim}
In sub-section 5.1 the MLP was described as our initial intention 
was to include it in this study. Thus, as suggested by the second 
reviewer (see first comment), the results obtained with this method 
have been included in the new version of this paper.

As far as the number of trees is related, TODO.
\end{verbatim}
%The first answer does not address the question. It only asks why is
%it described in 5.1 and not in 4.2. Probably the right response would
%be to move it to 4.2 - JJ
~\\
\noindent (3) \emph{As we known, tree-based mehods (e.g.,M5P and RF) themselve embed feature selection procedure. That is, some features are choosen to build trees. It is not fair enough to compare five methods in Table 3. }

### 2016-08-20 Response to reviewers.tex

\begin{verbatim}
THIS HAS TO BE DONE.
\end{verbatim}

~\\
\noindent (5) \emph{It is necessary to write that paper more concisely. }

\begin{verbatim}
Following your suggestion we have reorganized some parts of the 
text and several paragraphs have been rewritten in order to make 
them clearer and to improve its comprehension.

Finally, the paper has been completely revised and several 
typographic errors have been fixed.
\end{verbatim}
% But it says we should shorten the paper, not to reorganize it. The
% right response should be to say what parts have been shortened - JJ

@@

Our main contribution is, thus, to develop a methodology to 
process book sales data in order to first find out relevant 
variables and then use these variables to process data so that 
the publisher, using them, can estimate sales and from them order 
a specific print run, instead of standard ones, which are around 
300 copies for standard books and around 5000 for those that are 
considered, in advance, best sellers.

Also, in the next-to-last paragraph, we have laid out our 
methodology and the main contributions of this paper.
\end{verbatim}

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommendation systems
have been added to the future works section, at the end of Section 7 
(see page 19).
\end{verbatim}
% Page might change with revision, so check it at the end - JJ
~\\
\noindent (4) \emph{Some tables should be transfer to figures because there are too many figures. }

@@

Our main contribution is, thus, to develop a methodology to 
process book sales data in order to first find out relevant 
variables and then use these variables to process data so that 
the publisher, using them, can estimate sales and from them order 
a specific print run, instead of standard ones, which are around 
300 copies for standard books and around 5000 for those that are 
considered, in advance, best sellers.

Also, in the next-to-last paragraph, we have laid out our 
methodology and the main contributions of this paper.
\end{verbatim}

~\\
\noindent (2) \emph{sections 4.1 and 4.2 should be moved to section 2. }

\begin{verbatim}
Following your suggestion we have reorganized these sub-sections, 
moving them to section 2.
\end{verbatim}

@@

~\\
\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology by including a flowchart (see Figure 1 at 
page 6).
\end{verbatim}

### 2016-08-20 paper.tex
addressing part of 1st point of reviewer#1

  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
(predictive of) the class, yet uncorrelated with (not predictive of) each other''. This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.%Pablo: the Oxford dictionary accepts both (zed and sed), but the one with Z is the one that appears as main in the entry
 The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation. In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.

>>>>

  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
(predictive of) the class, yet uncorrelated with (not predictive of) each other''. This evaluator needs the numeric features to be transformed to nominal features first, by being discretized.%Pablo: the Oxford dictionary accepts both (zed and sed), but the one with Z is the one that appears as main in the entry
 The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation. For continuous class problems (regression), the correlation between the attributes is estimated based on a standard linear correlation
using the Pearson's correlation coefficient as given in Equation \ref{eq:corr} \cite{hall2000correlation}.

\begin{equation}
r_{XY}=\frac{\sum xy}{n\sigma_{x}\sigma_{y}}
\label{eq:corr}
\end{equation}

Where $X$ and $Y$ are two continuous variables expressed in terms
of deviation.
